Blocking-resistant communication\\through domain fronting

### 2015-02-07 docs/fronting.tex
Intro hacking.

\begin{abstract}
We describe ``domain fronting,'' a versatile censorship circumvention technique
that hides the remote endpoint of a communication.
Domain fronting works at the application layer, using HTTPS,
to communicate with a forbidden host
while appearing to communicate with some other host,
permitted by the censor.
The key idea is the use of different domain names at different layers of communication.
One domain appears on the ``outside'' of the HTTPS request---in the DNS request and
TLS Server Name Indication---while another domain appears
on the ``inside''---in the HTTP Host header, invisible to the
censor under HTTPS encryption.
A censor, unable to distinguish fronted and non-fronted traffic to a domain,
must choose between allowing circumvention traffic
and blocking the entire domain,
which results in expensive collateral damage.

@@

We as circumventors have in our favor the censor's
distaste for ``collateral damage'':
accidental overblocking committed in the course of trying to censor something else.
One way to win against censorship is to entangle circumvention traffic
with ordinary Internet traffic such that both must be blocked together,
or not at all.
If the ordinary traffic is valuable enough,
above the censor's tolerance for overblocking,
then the circumvention traffic will get through.

In this paper we describe ``domain fronting,'' a general-purpose technique
based on HTTPS that hides the true destination of a communication
from a censor.
Fronting works with many web services that host multiple domain names
behind an HTTPS frontend server.
These include such high-collateral-damage infrastructure as
big content delivery networks (CDNs)
and Google's panoply of services---a nontrivial fraction of the web.
(See Section~\ref{sec:survey} for a list of suitable services.)
Domain fronting can be used to tunnel traffic
to a general-purpose proxy,
so that circumvention is not limited only to HTTPS, nor to the domains of any specific web service.

The key idea of domain fronting is the use of
different domain names at different layers of communication.
In an HTTPS request, the destination domain name appears
in three places relevant to the discussion:
in the DNS query,
in the TLS Server Name Indication (SNI) extension~\cite[\S 3]{rfc6066},
and in the HTTP Host header~\cite[\S 14.23]{rfc2616}.
Usually, the same domain name appears in all three places.
In a domain-fronted request, however,
the DNS query and SNI carry one name (the ``front domain''),
while the HTTP Host header,
which is hidden from the censor by HTTPS encryption,
carries another (the actual destination).

@@

The censor can block neither the DNS request nor the SNI without
collaterally blocking the front domain.
The Host header is invisible to the censor,
but visible to the server receiving the HTTPS request,
which uses the header to internally route the request to its destination.
No traffic ever reaches the front domain,
which may be oblivious to the circumvention.
For those familiar with decoy routing~\cite{decoyrouting,telex,cirripede,tapdance},
domain fronting can be understood as
``decoy routing at the application layer.''
A fuller comparison with decoy routing appears in Section~\ref{sec:related-work}.

This Wget command shows domain fronting in action
on Google's infrastructure.
Here, an HTTPS request for \urll{www.google.com} has a Host header for
\urll{maps.google.com}, even though the SNI in the TLS handshake specifies
\texttt{www.google.com}.
The HTML in the response is that of Google Maps.

\noindent
\begin{quote}
\usefont{U}{cmtt}{m}{n}%
\$ wget -q -O - https://www.google.com/ \char`\\\\
\strut~~~~--header \textquotesingle{}Host: maps.google.com\textquotesingle{} | \char`\\\\
\strut~~~~grep -o \textquotesingle{}<title>.*</title>\textquotesingle{}\\
<title>Google Maps</title>
\end{quote}

>>>>

\begin{abstract}
We describe ``domain fronting,'' a versatile censorship circumvention technique
that hides the remote endpoint of a communication.
Domain fronting works at the application layer, using HTTPS,
to communicate with a forbidden host
while appearing to communicate with some other host,
permitted by the censor.
The key idea is the use of different domain names at different layers of communication.
One domain appears on the ``outside'' of an HTTPS request---in the DNS request and
TLS Server Name Indication---while another domain appears
on the ``inside''---in the HTTP Host header, invisible to the
censor under HTTPS encryption.
A censor, unable to distinguish fronted and non-fronted traffic to a domain,
must choose between allowing circumvention traffic
and blocking the entire domain,
which results in expensive collateral damage.

@@

Circumventors,
at a natural disadvantage because the censor controls the network,
have one point working in their favor:
the censor's distaste for ``collateral damage,''
accidental overblocking committed in the course of censorship.
Collateral damage is harmful to the censor,
because the overblocked content is economically or socially beneficial,
so the censor avoids it when possible.
(Any censor not willing to turn off the Internet completely
must derive \emph{some} benefit from allowing access,
which overblocking harms.)
One way to win against censorship is to entangle circumvention traffic
with other traffic, which is valuable enough to
exceed the censor's tolerance for overblocking.

In this paper we describe ``domain fronting,'' a general-purpose circumvention technique
based on HTTPS that hides the true destination of a communication
from a censor.
Fronting works with many web services that host multiple domain names
behind a frontend server.
These include such important infrastructure as
content delivery networks (CDNs)
and Google's panoply of services---a nontrivial fraction of the web.
(Section~\ref{sec:survey} is a survey of suitable services.)
The utility of domain fronting is not limited to HTTPS communication,
nor to accessing only the domains of a specific web service:
it works well as a domain-hiding component of a larger circumvention system,
an HTTPS tunnel leading to a general-purpose proxy.

The key idea of domain fronting is the use of
different domain names at different layers of communication.
In an HTTPS request, the destination domain name appears
in three relevant places:
in the DNS query,
in the TLS Server Name Indication (SNI) extension~\cite[\S 3]{rfc6066},
and in the HTTP Host header~\cite[\S 14.23]{rfc2616}.
Ordinarily, the same domain name appears in all three places.
In a domain-fronted request, however,
the DNS query and SNI carry one name (the ``front domain''),
while the HTTP Host header,
hidden from the censor by HTTPS encryption,
carries another (the covert, forbidden destination).

@@

The censor cannot block on the contents of the DNS request nor the SNI without
collaterally blocking the front domain.
The Host header is invisible to the censor,
but visible to the frontend server receiving the HTTPS request.
The frontend server uses the Host header internally to route the request
to its covert destination; no traffic ever reaches the putative front domain.
Domain fronting has many similarities with decoy routing~\cite{decoyrouting,telex,cirripede,tapdance};
it may be understood as
``decoy routing at the application layer.''
A fuller comparison with decoy routing appears in Section~\ref{sec:related-work}.

This Wget command demonstrates domain fronting
on Google, one of many fronting-capable services.
Here, the HTTPS request has a Host header for \urll{maps.google.com},
even though the DNS query and the SNI in the TLS handshake specify \urll{www.google.com}.
The response comes from \urll{maps.google.com}.

\noindent
\begin{quote}
\usefont{U}{cmtt}{m}{n}%
\$ wget -q -O - https://www.google.com/ \char`\\\\
\strut~~~~--header \textquotesingle{}Host:~maps.google.com\textquotesingle{} | \char`\\\\
\strut~~~~grep -o \textquotesingle{}<title>.*</title>\textquotesingle{}\\
<title>Google Maps</title>
\end{quote}
